MSHS COVID-19 Vaccinations

### 2021-12-10 Combined Dashboard Arrived and Sched Appts.Rmd
Update analysis reference file with 31-60 21 St General Surgery.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-11-22.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-11-22.xlsx"),
                           sheet = "Pod Mappings Simple")

# Store today's date
today <- Sys.Date() - 1
yesterday <- today - 1

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-12-10.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-12-10.xlsx"),
                           sheet = "Pod Mappings Simple")

# Store today's date
today <- Sys.Date()
yesterday <- today - 1
